Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-09-15 Draft/draft.tex
Honghao: minor changes

\begin{abstract}
	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$,
	where $r$ is the smallest multiplicative generator of $\Zd$.
	The construction of the correlation uses the embedding procedure
	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$ Cambridge University Press, $2019$).
	Since there are 
	infinitely many prime numbers whose smallest multiplicative generator
	is at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimensions.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics and with the only assumption that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

@@

        \appd{(2n\ep_1 + \ep_2} \left(\Pi_{i=1}^k V_i\right) 

@@

The group $\Pg_0$ is a conjugacy group (\cref{def:spe_conj_grp}), and is defined below.
The purpose of this step is to embed $\Pg$ into a group where all the
generators are of order-$2$, because
it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single binary generator. 
On the other hand, a homomorphism from $\Pg_0$ to a solution group can be easier to find because all the generators of $\Pg_0$ are binary.
\begin{definition}	
\label{def:g0}
	Let the set $S_0$ be 
	\begin{align*}
		S_0 = \{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5,
	\end{align*}
	and the set $R_0$ be the union of 
	\begin{align*}
	&R_{base} = \{s^2 = e | s \in S\},\\
	&R_{u} = \{ u_3 = u_2o_1u_2 \quad u_4 = u_2o_2u_2 \quad 
	u_5 = u_1u_3u_1 \quad o_2 = u_1u_4u_1 \quad u_5 = o_1 o_r o_1\},
	\end{align*}
	and 
	\begin{align*}
	R_o = 
	\begin{cases} 
	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1 \quad o_{2+2j} = o_2o_{1+2j}o_2\} \quad \text{ if $r$ is even },\\
	\{o_3 = o_2o_1o_2\} \cup \bigcup_{j=1}^{(r-3)/2}\{
	 o_{2+2j} =o_1o_{1+2j}o_1 \quad o_{3+2j} = o_2o_{2j+2}o_2 \}\quad\text{ if $r$ is odd }.
	\end{cases}
	\end{align*}
	The group $\Pg_0$ is a group with presentation $\ip{R_0:S_0}$.
\end{definition}
The special generators of $\Pg_0$ are $o_1, o_2, u_1$ and $u_2$ because the product $o_1o_2$ behaves similarly as $o$,
and the product $u_1u_2$ behaves similarly as $u$.
Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$,
as proved in the next proposition.
\begin{proposition}
    \label{prop:g0}
	The group $\Pg$ is embedded in $\Pg_0$.
	Furthermore, the generators of $\Pg_0$ satisfy the relations 
	\begin{align}
	    \label{eq:uo_comm}
	    &(u_1u_2) o_2 (u_2u_1) = o_2 \\ 
	    \label{eq:uo_rel}
		&(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
	\end{align}
	for any $ j \in \N$.
\end{proposition}
\begin{proof}
    We prove \cref{eq:uo_comm} first. It is easy to see that
    \begin{align}
        u_1 (u_2o_2u_2) u_1 = u_1u_4u_1 =o_2.
    \end{align}

@@

%-------------------------------------
\subsection{The group $\Gamma$}
\label{sec:gamma}
%-------------------------------------
The group $\Gamma$ is a solution group,
so all the generators of $\Gamma$ are of order-$2$
and all the relations are linear relations.
Moreover, the linear relations can be combined
to recover the conjugacy relations in $R_1$.
\begin{definition}
\label{def:gamma}
Define the set $S$ to be 
\begin{align*}
	S = \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
\end{align*}
and the set $R$ to be the union of the following
sets of linear relations:
\begin{itemize}
\item for each $i = 1 \dots r+5$:
\begin{align*}
	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
	%&g_2 a_i w_i = e \\
	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
\end{align*}
\item for each $ \bc = (i,j,k) \in C(r)$:
\begin{align*}
	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
\end{align*}
\item 
$
	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
$
\item $R_J = \{ J s J s = e \vert s \in S\} \cup \{J^2 = e\}$,
\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
\end{itemize}
The group $\Gamma$ is a group with the presentation
$\ip{S \cup \{J\} : R}$.
\end{definition}

@@

	Using \cref{eq:o1,eq:o2}, it is straightforward to see that $\Psi_0(a_j)\x \Psi_0(a_j) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ for $j = 1,2$.
	Before checking the two cases $j=3$ and $j=4$, we can use \cref{eq:u1u2} to derive that
	\begin{align*}
		\Psi_0(a_3 a_4) \x\Psi_0(a_3 a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}.
	\end{align*}
	The eigenvectors of $\Psi_0(a_3 a_4)$ are $\ket{u_k}$,
	for $0 \leq k \leq d-2$,
	and $\ket{u_k}$ are defined by
    \begin{align*}
        \ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
    \end{align*}
    Hence we can express $\ket{x_{r^j}}$ in terms of $\ket{u_k}$ as 
    \begin{align*}
        \ket{x_{r^j}} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
    \end{align*}
    Then using the expression of $\Psi_0(a_4)$ from \cref{def:rep_g0},
    we can deduce that
    \begin{align*}
        \Psi_0(a_4) \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} \Psi_0(a_4) \left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
        \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
        =&\frac{1}{\sqrt{d-1}} \left(\ket{u_0} + (-1)^j\ket{u_{(d-1)/2}}  + 
        \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_{d-1-k}} + \omega_{d-1}^{jk} \ket{u_{k}})\right) \\
        =& \ket{x_{r^{d-1-j}}}.
    \end{align*}
    Note that the expression of $\Psi_0(a_4)$ can also be found in
    \cref{eq:u2}, as $\Psi(a_4) = \1_{W_2} \x \1_{W_2} \x \Psi_0(a_4)$.
    Consequently, we can show that $\Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ 
    because
    \begin{align*}
        \Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} &= \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \Psi_0(a_4)\x  \Psi_0(a_4) \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} \\
        &= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}}\\ &=\ket{\tpsi}^{\EXT},
    \end{align*}
	Combining it with the fact that $\Psi_0(a_3 a_4) \x \Psi_0(a_3 a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$, we can conclude that
	$\Psi_0(a_3) \x \Psi_0(a_3) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$.
\end{proof}

@@

\section*{Acknowledgment}
The author is deeply grateful to his PhD advisor, Carl Miller, for the enlightening discussions with him, his patient guidance and useful critiques through this
project. His original idea about 
combining a linear system game with a Bell inequality and characterizing prime numbers
by their primitive roots are invaluable to
this work. He also helped the author with the design
of the extended weighted CHSH test
and the editing of the draft.

>>>>

\begin{abstract}
	We show that for any prime odd integer $d$, there exists a correlation of size $\Theta(r)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$,
	where $r$ is the smallest multiplicative generator of $\Zd$.
	The construction of the correlation uses the embedding procedure
	proposed by Slofstra (\textit{Forum of Mathematics, Pi.} Vol.~$7$, ($2019$)).
	Since there are 
	infinitely many prime numbers whose smallest multiplicative generators
	are at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
The certification of a quantum device is an important building block
for many quantum information processing tasks, especially
when the devices are provided by some untrusted vendor.
We would like such certification to be done based solely on
the observed measurement statistics and with the only assumption that
any local device cannot communicate their own
inputs to the other local devices. 
The measurement statistics are referred to as correlations.

@@

        \appd{2n\ep_1 + \ep_2} \left(\Pi_{i=1}^k V_i\right) 

@@

The group $\Pg_0$ is a conjugacy group (\cref{def:spe_conj_grp}), and is defined below.
The purpose of this step is to embed $\Pg$ into a group where all the
generators are of order-$2$, because
it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single binary generator. 
On the other hand, a homomorphism from $\Pg_0$ to a solution group can be easier to find because all the generators of $\Pg_0$ are binary.
\begin{definition}	
\label{def:g0}
	Let the set $S_0$ be 
	\begin{align*}
		S_0 = \{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5,
	\end{align*}
	and the set $R_0$ be the union of 
	\begin{align*}
	&R_{base} = \{s^2 = e | s \in S\},\\
	&R_{u} = \{ u_3 = u_2o_1u_2, \quad u_4 = u_2o_2u_2, \quad 
	u_5 = u_1u_3u_1, \quad o_2 = u_1u_4u_1, \quad u_5 = o_1 o_r o_1\},
	\end{align*}
	and 
	\begin{align*}
	R_o = 
	\begin{cases} 
	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1, \quad o_{2+2j} = o_2o_{1+2j}o_2\}  &\text{ if $r$ is even },\\
	\{o_3 = o_2o_1o_2\} \cup \bigcup_{j=1}^{(r-3)/2}\{
	 o_{2+2j} =o_1o_{1+2j}o_1, \quad o_{3+2j} = o_2o_{2j+2}o_2 \} &\text{ if $r$ is odd }.
	\end{cases}
	\end{align*}
	The group $\Pg_0$ is a group with presentation $\ip{R_0:S_0}$.
\end{definition}
The special generators of $\Pg_0$ are $o_1, o_2, u_1$ and $u_2$ because the product $o_1o_2$ behaves similarly as $o$,
and the product $u_1u_2$ behaves similarly as $u$.
Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$,
as proved in the next proposition.
\begin{proposition}
    \label{prop:g0}
	The group $\Pg$ is embedded in $\Pg_0$.
	Furthermore, the generators of $\Pg_0$ satisfy the relations 
	\begin{align}
	    \label{eq:uo_comm}
	    &(u_1u_2) o_2 (u_2u_1) = o_2 \\ 
	    \label{eq:uo_rel}
		&(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
	\end{align}
	for any $ j \in \N$.
\end{proposition}
\begin{proof}
    We prove \cref{eq:uo_comm} first. It is easy to see that
    \begin{align}
        u_1 (u_2o_2u_2) u_1 = u_1u_4u_1 =o_2.
    \end{align}

@@

%-------------------------------------
\subsection{The group $\Gamma$}
\label{sec:gamma}
%-------------------------------------
The group $\Gamma$ is a solution group,
so all the generators of $\Gamma$ are of order-$2$
and all the relations are linear relations.
Moreover, the linear relations can be combined
to recover the conjugacy relations in $R_1$.
\begin{definition}
\label{def:gamma}
Define the set $S$ to be 
\begin{align*}
	S = \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
\end{align*}
and the set $R$ to be the union of the following
sets of linear relations:
\begin{itemize}
\item for each $i = 1 \dots r+5$:
\begin{align*}
	R_i =  \{ &a_i = b_ic_i = f_0d_i,\quad
	%&g_2 a_i w_i = e \\
	f_0 f_1 f_2 = e, \quad b_i f_2 p_{i,1} = e, \quad p_{i,1} p_{i,2} p_{i,3} = e,\\
	&f_0 p_{i,3} p_{i,4} = e, \quad c_i p_{i,4} p_{i,5} =e, \quad f_1 p_{i,2} p_{i,5} = e\},
\end{align*}
\item for each $ \bc = (i,j,k) \in C(r)$:
\begin{align*}
	R_{\bc} = \{&h_{jk}b_j c_k = e, \quad
	d_i q_{\bc,1} f_2 = e, \quad b_j f_2 q_{\bc,2} = e, \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e,\\
	&d_i q_{\bc,4} q_{\bc,5} = e, \quad c_k q_{\bc,5} q_{\bc,6} =e, \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
\end{align*}
\item 
$
	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e, \quad m_0 m_1 m_2 = e, \quad
	f_0 g_2 m_0 = e, \\ \indent f_2 g_0 m_1 = e, \quad f_1 g_1 m_2 = J\},
$
\item $R_J = \{ J s J s = e \vert s \in S\} \cup \{J^2 = e\}$,
\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
\end{itemize}
The group $\Gamma$ is a group with the presentation
$\ip{S \cup \{J\} : R}$.
\end{definition}

@@

	Using \cref{eq:o1,eq:o2}, it is straightforward to see that $\Psi_0(a_j)\x \Psi_0(a_j) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ for $j = 1,2$.
	Before checking the two cases $j=3$ and $j=4$, we can use \cref{eq:u1,eq:u2} to derive that
	\begin{align*}
		\Psi_0(a_3 a_4) \x\Psi_0(a_3 a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}.
	\end{align*}
	The eigenvectors of $\Psi_0(a_3 a_4)$ are $\ket{u_k}$,
	for $0 \leq k \leq d-2$,
	and $\ket{u_k}$ are defined by
    \begin{align*}
        \ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
    \end{align*}
    Hence we can express $\ket{x_{r^j}}$ in terms of $\ket{u_k}$ as 
    \begin{align*}
        \ket{x_{r^j}} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
    \end{align*}
    Then using the expression of $\Psi_0(a_4)$ from \cref{def:rep_g0},
    we can deduce that
    \begin{align*}
        \Psi_0(a_4) \ket{x_{r^j}} =& \frac{1}{\sqrt{d-1}} \Psi_0(a_4) \left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
        \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
        =&\frac{1}{\sqrt{d-1}} \left(\ket{u_0} + (-1)^j\ket{u_{(d-1)/2}}  + 
        \sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_{d-1-k}} + \omega_{d-1}^{jk} \ket{u_{k}})\right) \\
        =& \ket{x_{r^{d-1-j}}}.
    \end{align*}
    Note that the expression of $\Psi_0(a_4)$ can also be found in
    \cref{eq:u2}, as $\Psi(a_4) = \1_{W_2} \x \1_{W_2} \x \Psi_0(a_4)$.
    Consequently, we can show that $\Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$ 
    because
    \begin{align*}
        \Psi_0(a_4) \x \Psi_0(a_4) \ket{\tpsi}^{\EXT} &= \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} \Psi_0(a_4)\x  \Psi_0(a_4) \ket{x_{r^j}} \ket{x_{r^{d-1-j}}} \\
        &= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{x_{r^{d-1-j}}} \ket{x_{r^{j}}}\\ &=\ket{\tpsi}^{\EXT},
    \end{align*}
	Combining it with the fact that $\Psi_0(a_3 a_4) \x \Psi_0(a_3 a_4) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$, we can conclude that
	$\Psi_0(a_3) \x \Psi_0(a_3) \ket{\tpsi}^{\EXT} = \ket{\tpsi}^{\EXT}$.
\end{proof}

@@

\section*{Acknowledgment}
The author is deeply grateful to his PhD advisor, Carl Miller, for the enlightening discussions with him, his patient guidance and useful critiques through this
project. His original ideas about 
combining a linear system game with a Bell inequality and characterizing prime numbers
by their primitive roots are invaluable to
this work. He also helped the author with the design
of the extended weighted CHSH test
and the editing of the draft.
